**Best practices for applying machine learning to bacterial 16S rRNA gene sequencing data**

### 2019-08-26 submission/manuscript.Rmd
add training time subsampling resutls

__The computational efficiency of each ML model.__ We compared the training times of the seven ML models. As expected, the training times increased with the complexity of the model and the number of tuned hyperparameter settings. Also, the linear models trained faster than non-linear models [Figures S1-S2; Figure 5]. When we subsetted the size of the training dataset, we observed a [linear, quadratic, etc] relationship between the size of the dataset and the training time for the random forest model.

>>>>

__The computational efficiency of each ML model.__ We compared the training times of the seven ML models. As expected, the training times increased with the complexity of the model and the number of tuned hyperparameter settings. Also, the linear models trained faster than non-linear models [Figures S1-S2; Figure 5]. When we subsetted the size of the training dataset, we observed an exponential relationship between the size of the dataset and the training time for the random forest model [Figure S5].
